\documentclass{article}


\usepackage{PRIMEarxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{fancyhdr}       % header
\usepackage{graphicx}       % graphics
\graphicspath{{media/}}     % organize your images and other figures under media/ folder


% stuff Spencer added
\usepackage{amsthm} % for proof and theorem environments
\usepackage{amsmath} % for math text

\newtheorem{theorem}{Theorem}[section]
%Header
\pagestyle{fancy}
\thispagestyle{empty}
\rhead{ \textit{ }} 

% Update your Headers here
\fancyhead[LO]{Running Title for Header}
% \fancyhead[RE]{Firstauthor and Secondauthor} % Firstauthor et al. if more than 2 - must use \documentclass[twoside]{article}



  
%% Title
\title{A template for Arxiv Style
%%%% Cite as
%%%% Update your official citation here when published 
\thanks{\textit{\underline{Citation}}: 
\textbf{Authors. Title. Pages.... DOI:000000/11111.}} 
}

\author{
  Author1, Author2 \\
  Affiliation \\
  Univ \\
  City\\
  \texttt{\{Author1, Author2\}email@email} \\
  %% examples of more authors
   \And
  Author3 \\
  Affiliation \\
  Univ \\
  City\\
  \texttt{email@email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}


\begin{document}
\maketitle


\begin{abstract}
Detecting shared neural activity across individuals experiencing the same 
naturalistic stimulus can reveal stimulus-driven brain responses, inform on 
brain regions' 
functional roles, and identify potential clinical biomarkers.
Intersubject correlation (ISC) includes the primary methods
for detecting voxelwise 
regions of shared response and quantifying subject-level variability.
However, ISC analyses require thousands of voxelwise tests, leading to 
multiple-comparison problems, and even nonparametric resampling methods 
often produce liberal sampling distribution which inflate false positives.
ISC methods treat voxels independently and lack 
principled ways to incorporate spatial structure.
We propose a model-based alternative to ISC that simultaneously estimates the 
shared neural response function and spatial activation patterns using a 
Gaussian process framework coupled with a Bayesian spatial sparsity prior 
inspired by the horseshoe prior.
We examine the properties of this prior—designed to induce stronger shrinkage 
than the standard horseshoe—and evaluate the model’s performance in simulations 
and real fMRI data.
The Bayesian model provides natural uncertainty quantification of the 
shared response function, and in the analyses it demonstrates better control 
of false positives 
relative to ISC approaches.
\end{abstract}


% keywords can be removed
\keywords{First keyword \and Second keyword \and More}

\include{manuscript}
%Bibliography
\bibliographystyle{unsrt}  
\bibliography{references}  


\end{document}
